Untitled

### 2018-08-09 MSOAmodel.Rmd
Complete re-factor
The code was turning into a complete mess and it wasn't clear what was happening at all and definitely not reproducible. I rewrote everything to simply the code and reduce the complexity of the workspace. I focussed on getting a few key model types and showing how they work and how they don't. The new code is much easier to understand and run.

@@

test <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )
test1 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )

test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )

@@

```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")

@@

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

@@

 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)
```

#Make modelling dataframe

The variables are

mean deprivation decile
Affordability

@@

MSOAdep <- LSOADep %>%
  select(LSOA_CODE, Rank = Rank..where.1.is.most.deprived., Decile = Decile..where.1.is.most.deprived.10..of.LSOAs.) %>%
  left_join(select(EW2, MSOA11CD, ECODE), by = c("LSOA_CODE"="ECODE")) %>%
  select(-LSOA_CODE) %>%
  group_by(MSOA11CD) %>%
  summarise_all(mean)

BootDeets <- BootStrapRES %>% 
  map_df(~.x %>%
           mutate(Reference = MedianHomes < MedianLUPs,
                  MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
           select(MSOA11CD, MeanPropPrice, Reference, ID)) %>%
  left_join(select(IncomeEst, MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  left_join(MSOAdep, by = "MSOA11CD") %>%
  mutate(AffordRatio  = MeanPropPrice/Yearly.income,
         AffordRatio2 = AffordRatio^2,
         AffordRatio3 = AffordRatio^3)

rm(MSOAdep)

#Why do some have 2000?
test <- BootDeets %>%
  group_by(MSOA11CD) %>%
  summarise(Majority = sum(Reference, na.rm = T)/1000,
            Total = n())

BootDeetsMean <- BootDeets %>%
  select(MSOA11CD, Reference, Decile, AffordRatio) %>%
  group_by(MSOA11CD) %>%
  summarise_all(mean) %>%
  mutate(Reference = Reference>0.5)

set.seed(1983)
TestResample <- 1:50 %>% map(~  resample_partition(BootDeetsMean, c(test = 0.1, train = 0.9)))

OpenFormula <- as.formula(Reference~ AffordRatio+ Decile)

BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))

sum(Accdf$Accuracy>Accdf$AccuracyNull)

mean(Accdf$Accuracy)

CoeffsMega <- 1 %>%
  map_df(~{
    print(.x)
    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  OpenFormula)

    #needs to be mapped again to extract every model not just the first 50!
    Out <- 1:length(BootMod) %>% map_df(~
                          BootMod[[.x]] %>% tidy %>% mutate(ID = .x)               
                                        )%>%
      mutate(Sample = .x)
  })

@@

>>>>

#LAD quartiles are wrong

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")
test <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = "class"  )

ChelTest1 <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )

test2 <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = c("MSOA11CD", "class"))

MSOAList <- unique(test2$MSOA11CD) %>%
  map(~{
test2 %>%
  filter(MSOA11CD == .x)
})

test3 <- MSOAList[[21]] %>%
  CleanForPlotClassDiff

MSOAList[[21]] %>%
CleanForPlotClassDiff()  %>%
PlotClassDiff(., "Kensington and Chelsea by MSOA")

test %>%
  mutate(LowUse = Homes) %>%
  CleanForPlotClassDiff()  %>%
  PlotClassDiff(., "Kensington and Chelsea full borough")

test %>%
#  mutate(LowUse = Homes) %>%
  CleanForPlotClassDiff2()  %>%
  PlotClassDiff(., "Kensington and Chelsea full borough")

CleanForPlotClassDiff2 <- function(df){ #relative to the homes distrib
  df %>% 
  group_by(ID, class) %>%
  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(RatioExvsAct = LowUse/sum(LowUse),
         HomesRatio = Homes/sum(Homes),
         RatioExvsAct = (RatioExvsAct/HomesRatio)-1)
}

@@

PropertyTypes <- c("D", "S", "T", "F")
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")

@@

  test <- ls(pattern = "DATA") %>% map_df(~
 data.frame(LAD = .x, LSOA = get(.x) %>% nrow(),Homes = sum(get(.x)$Homes, na.rm = T))) %>%
    arrange(Homes)

  newLADs <- newLADs[match(test$LAD, newLADs)] %>% .[!is.na(.)]

  #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 501, type=NULL, PropertyTypes, GroupVars = "MSOA11CD", Limit =1.3e5  )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      gc()
      }) 
  }

@@

 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)

@@

library(Rtsne)

# dfmat <- BootDeetsMean %>%
#   select(AffordDiff, Decile, AffordRatio, AffordRatio2, DecileDiff) %>%
#   as.matrix()

dfmat <- ModelMSOAdf %>%
  select( Tourism, AffordRatio, AffordRatio2) %>%
  as.matrix()

set.seed(12358)
TsnecorOut1 <-dfmat  %>%
  Rtsne(verbose = TRUE, eta = 1, max_iter = 5000, perplexity = 50, check_duplicates = FALSE)

# tsne_corplot <- data.frame(x1 = TsnecorOut1$Y[,1],
#                         y1 = TsnecorOut1$Y[,2]) %>%
#   bind_cols(BootDeetsMean) %>%
#   mutate(MedianCheck = MSOAHomesMedian<MSOALowUseMedian)

tsne_corplot <- data.frame(x1 = TsnecorOut1$Y[,1],
                        y1 = TsnecorOut1$Y[,2]) %>%
  bind_cols(ModelMSOAdf)

tsne_corplot %>%
    ggplot() +
  geom_point(aes(x=x1, y=y1, color= TourDepCat==1|TourDepCat==2))

BootDeetsMean %>%
  ggplot(aes(x = LowUseConc, y = AffordDiff, colour = Reference)) + geom_point()

BootDeetsMean %>%
  filter(sales <1) %>%
  ggplot(aes(x = sales, y = LowUse, colour = Reference)) + geom_point()

@@

#Sample quantiles

```{r}
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)

PriceCounts<- EW2 %>%
  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0)

#Create a list of vectors by LSOA
setwd(basewd)
 LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
   print(.x)
    prices %>%
      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
             X5 %in% c("D", "S", "T", "F")) %>%
      pull(X2)
 })

 names(LSOAPriceList) <- PriceCounts$LSOA11CD
saveRDS(LSOAPriceList, "LSOAPriceList2.rds")

LSOAPriceList <- readRDS("LSOAPriceList2.rds")

StratifiedBoot <- function(dataList, LSOAcode, SamplesVect, samples = 1000){
  #datadf
 1: samples %>% map_df(~{
   print(.x)
  SubData <- 1:length(LSOAcode) %>% map(~{
    #print(.x)
    dataList[[LSOAcode[.x]]] %>%
      sample(., SamplesVect[.x], replace = TRUE)

    }) %>% unlist

  SubData%>%
       quantile(.) %>% t %>% as.data.frame %>% setNames(names(.) %>% make.names) %>%
      mutate(mean = mean(SubData),
             ID = .x)
 }) 
}

#Subset list to only the LADs used in analyis
LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
PriceCounts2 <- PriceCounts %>%
  filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))

AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)

test <- LSOAPriceList %>% map_int(length(.x))

#MSOA Quartiles

I'm not sure this is useful

```{r}
#Create a list of vectors where each element of the list is an MSOA and the vector elements are its LSOA
 LSOAinMSOA <- unique(PriceCounts$MSOA11CD) %>% map(~{
   print(.x)
    PriceCounts %>%
      filter(MSOA11CD==.x) %>%
      pull(LSOA11CD)
 })
 #name the elements of the list
 names(LSOAinMSOA) <- unique(PriceCounts$MSOA11CD)

 #Create a bootstrap for each of the MSOA

 MSOABootQuartiles <- unique(PriceCounts$MSOA11CD) %>% map_df(~{
   print(.x)
   PriceCounts2 <- PriceCounts %>%
     filter(MSOA11CD == .x)

   LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% PriceCounts2$LSOA11CD]

   StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 100) %>%
     mutate(MSOA11CD=.x)

 })

 saveRDS(MSOABootQuartiles, "MSOABootQuartiles.rds")

 MSOABootQuartiles2 <- MSOABootQuartiles %>%
   select(-X0.,-X100.) %>%
   group_by(MSOA11CD) %>%
   summarise_all(funs(mean, sd)) %>%
   mutate(X25Perc = X25._sd/X25._mean,
          X50Perc = X50._sd/X50._mean,
          X75Perc = X75._sd/X75._mean)  %>%
   left_join(., EW2%>%
               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
   left_join(., IncomeEst) %>%
   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM) %>%
   mutate(AffordRatio = MedianPrice/Yearly.income,
          AffordRank = percent_rank(AffordRatio))
```

#Local value

Here I create a graph of the MSOA. 
I calculate the avereage distance by LAD.
I then use that distance to find all the MSOA within that jump distance.
I then calculate the mean and quartiles of the local area for each MSOA
From there I can calculate the local area affordability and thus the relative local area affordability

 MSOAAdjacency <- readShapeSpatial(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))

 test <- poly2nb(MSOAAdjacency)

 MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)

#Add MSOA codes so that they are added as the vertex names
colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd

MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")

#Add in Lad

MSOAgraph <- set_vertex_attr(MSOAgraph, 
                name = "LAD11CD", 
                value = MSOAtoLAD$LAD11CD[match(get.vertex.attribute(MSOAgraph, "name"),
                                          MSOAtoLAD$MSOA11CD)]
                )

#Subset by LAD into a list of graphs

Subgraph <- function(g, KeepNodes){

  VertexNames <-get.vertex.attribute(g, "name")
  VertexNames<- VertexNames[!(VertexNames %in% KeepNodes)]

g2 <- delete_vertices(g, VertexNames)

g2
}

AllLADsGraph <- unique(MSOAtoLAD$LAD11CD) %>% map(~{
  KeepNodes <-MSOAtoLAD %>%
  filter(LAD11CD ==.x)
KeepNodes2 <- KeepNodes$MSOA11CD

  Subgraph(MSOAgraph, KeepNodes2)
})

#name the elements by the LAD represented
names(AllLADsGraph) <- unique(MSOAtoLAD$LAD11CD)

#calculate mean distance and diameter of each lad
MSOAconnections <- AllLADsGraph %>% map_df(~{

  tibble(distance = mean_distance(.x), diameter = diameter(.x), MSOA = vcount(.x))

}) %>%
  mutate(LAD11CD = names(AllLADsGraph)) %>%
  filter(MSOA !=1) #removes city of london which only has a single MSOA and so can't be included in the calc

MSOAconnections %>%
  ggplot(aes(x=diameter )) + geom_density()

#Using mean distance is best
summary(MSOAconnections$distance)
summary(MSOAconnections$diameter)

# find names of local MSOA using an x jump distance
EgoSize <- tibble(ego_size = ego_size(MSOAgraph, 2), MSOA11CD = get.vertex.attribute(MSOAgraph, "name")) %>%
  left_join(MSOAtoLAD)
##Ego size of jump two has a mean almost identical to the mean number of MSOA in a LAD. However the Ego size is less skewed.
mean(EgoSize$ego_size)

MSOAtoLAD %>%
  group_by(LAD11CD) %>%
  summarise(counts = n(),
            LAD11NM = first(LAD11NM)) %>%
  pull(counts) %>% mean

test <-  tibble(MSOA11CD = ego(MSOAgraph, 1, nodes = "E02000001")[[1]] %>% names) %>%
  left_join(MSOAtoLAD)

##names of the MSOA in each area.
MSOAEgoList <- ego(MSOAgraph, 2) %>%map(~names(.x))
names(MSOAEgoList) <- get.vertex.attribute(MSOAgraph, "name")

```{r}
#Create a list of vectors where each element of the list is an MSOA and the vector elements are its LSOA
 LSOAinMSOAEgo <- MSOAEgoList %>% map(~{
   #print(.x)
    PriceCounts %>%
      filter(MSOA11CD %in% .x) %>%
      pull(LSOA11CD)
 })

 ##name the elements of the list
 names(LSOAinMSOAEgo) <- names(MSOAEgoList)

 ##Create a bootstrap for the ego of each MSOA
 NeighbourhoodQuartiles <- names(MSOAEgoList) %>% map_df(~{

   print(.x)
   target <- MSOAEgoList[[.x]]
   PriceCounts2 <- PriceCounts %>%
     filter(MSOA11CD %in% target)

   LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% PriceCounts2$LSOA11CD]

   Out <-StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 10) %>%
     mutate(MSOA11CD=.x)

   Out

 })

Do westminster and lambeth fall into each others local area?
need to check and make sure they do!
```{r}
#Calculate mean local income
LocalIncome <- names(MSOAEgoList) %>% map(~{
  print(.x)
#.x <- "E02000001"
Group <-MSOAEgoList[[.x]]

Incomest2 <- IncomeEst %>%
  left_join(select(MSOAtoLAD, MSOA11CD, Homes),  by="MSOA11CD")

Out <- Incomest2 %>%
  filter(MSOA11CD %in% .x) %>%
  summarise(LocalIncome =sum(Yearly.income* Homes)/sum(Homes)) %>% pull()

Out
}) %>% unlist %>%
  tibble(MSOA11CD = names(MSOAEgoList), LocalIncome = .)

LocalAfford <-NeighbourhoodQuartiles %>%
  select(-ID,-X0., -X100.) %>%
    group_by(MSOA11CD) %>%
  summarise_all(funs(mean, sd, min, max)) %>%
  mutate(perc = X50._sd/X50._mean) %>%
  left_join(LocalIncome, by = "MSOA11CD") %>%
  mutate(LocalAfford = X50._mean/LocalIncome) %>%
  select(MSOA11CD, MedianLocalHomesPrice = X50._mean, LocalAfford)

```{r}
LupPerc <- ls(pattern= "DATA") %>% map_df(~{
  get(.x) %>% select(MSOA11CD, LowUse, Homes)

}) %>%
  group_by(MSOA11CD) %>%
  summarise_all(sum) %>%
  mutate(LowUsePerc = LowUse/(LowUse+Homes),
         Q1 = LowUsePerc>0.033,
         Q2 = LowUsePerc>0.02,
         Top90 = LowUsePerc>0.058)

#Top quartile of LUPS
quantile(LupPerc$LowUsePerc)
quantile(LupPerc$LowUsePerc, prob = seq(0, 1, length = 11))

MSOABootQuartiles2 <- MSOABootQuartiles %>%
   select(-X0.,-X100.) %>%
   group_by(MSOA11CD) %>%
   summarise_all(funs(mean, sd)) %>%
   mutate(X25Perc = X25._sd/X25._mean,
          X50Perc = X50._sd/X50._mean,
          X75Perc = X75._sd/X75._mean)  %>%
   left_join(., EW2%>%
               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
   left_join(., IncomeEst) %>%
   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM)  %>%
  left_join(LocalAfford, by = "MSOA11CD") %>%
  left_join(LupPerc, by = "MSOA11CD")%>%
  filter(!is.na(LowUse)) %>%
   mutate(AffordRatio = MedianPrice/Yearly.income,
          AffordLocalRatio = AffordRatio/LocalAfford,
          AffordRank = percent_rank(AffordRatio),
          AffordLocalRank = percent_rank(AffordLocalRatio),
          LowUseRank = percent_rank(LowUse)>0.75)

MSOABootQuartiles2 %>%
  ggplot(aes(x= AffordRatio , y = AffordLocalRatio, colour = LowUseRank)) + geom_point()

#Quadrant

```{r}
  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
                                    summarise(MedianHomes = first(MedianHomes),
                                              MeanHomes = first(MeanHomes),
                                              MedianLUPs = first(MedianLUPs),
                                              MeanLUPs = first(MeanLUPs),
                                              LAD11CD= first(LAD11CD),
                                              HighVal = sum(HighVal),
                                              Homes = sum(Homes),
                                              LowUse = sum(LowUse)) %>%
                                    group_by(LAD11CD) %>%
                                    summarise_all(., mean, na.rm = TRUE) %>%
                                      select(-ID)
  )

BootDeets2 <- BootDeets %>%
  mutate(MedianPercDiff = (MedianLUPs-MedianHomes)/MedianHomes,
         PercLowUse = LowUse/Homes,
         RankLowUse = percent_rank(PercLowUse),
         RankMedianDiff = percent_rank(MedianPercDiff),
         Catagory = case_when( 
           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
           TRUE ~ 4 #Low low use low price difference
         ) %>% as.factor)%>%
  left_join(EW2 %>%
  group_by(LAD11CD, LAD11NM) %>%
  summarise(TotMSOA = n(),
         Homes = sum(Homes)) %>%
  arrange(-TotMSOA) %>%
  summarise(TotMSOA = first(TotMSOA),
            LAD11NM = first(LAD11NM)), by = "LAD11CD")

BootDeets2 %>%
  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Catagory)) + geom_point()

test <- MSOABootQuartiles2 %>%
  left_join(select(BootDeets2, LAD11CD, Catagory), by = "LAD11CD")

 %>%
  ggplot(aes(x= AffordRank , y = AffordLocalRank, colour = Catagory)) + geom_point()

### 2018-08-09 OldCode.Rmd
Complete re-factor
The code was turning into a complete mess and it wasn't clear what was happening at all and definitely not reproducible. I rewrote everything to simply the code and reduce the complexity of the workspace. I focussed on getting a few key model types and showing how they work and how they don't. The new code is much easier to understand and run.

Are LUPS concentrated in specific areas?
  They are more concentrated than homes in general
Are LUPs more or less expensive?
  They tend to be concentrated in more expensive areas
Are High value LUP LADS predictable?
   They are predictable using number of vacants deprivation and price
What is the relationship between LUPs and affordability?
   A bath Tub curve
What would the revenue from an empty homes tax be in the current situation?
  A lot

@@

```{r}
# 
# setwd(file.path(RegionsComp, "Region Wales"))
# list.files()
# 
# #Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
# 
# CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse =c(8:13,15))
# 
# MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(4:8))
# 
# 
# #includes the zero class which is descibeed as 
# #ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
#   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
#     StructureData()
# 
# #Strangely low numbers checking
# # PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
# #   StructureData(lowuse = c(3,5:6))
# 
# #It seems Conwy really is this short on the discounts  
# ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
#   rename(Postcode = geo_postcode) %>%
#   mutate(Postcode = sub(" ", "", Postcode)) %>%
#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
#   StructureData(lowuse = c(2,4))
# 
# DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
#     StructureData(c(8:9,11,13))
# 
# WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
#     StructureData(2:5)
# 
# #Pembrokeshire didn't send all the data
# PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
#     StructureData(3)
# 
# FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
#     StructureData()

@@

@@

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>% # ward code is used for consistency
  summarise(
    #MSOA11CD = first(MSOA11CD), #MSOA is kept to allow joining of income
    LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))

@@

unaffordLAD <- unafford %>%
  rename(LAD11CD = Local.authority.code) %>%
  group_by(LAD11CD) %>%
  mutate(TotInc = Yearly.income*Pop) %>%
  summarise(TotInc = sum(TotInc),
            Pop = sum(Pop)) %>%
  mutate(meanInc = TotInc/Pop)

@@

CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

@@

MakeLeaflet(ConwyDATA)

>>>>

Are LUPS concentrated in specific areas?
  They are more concentrated than homes in general
  Spatial Auto-Correlation?
Are LUPs more or less expensive?
  They tend to be concentrated in more expensive areas
Are High value LUP LADS predictable?
   They are predictable using number of vacants deprivation and price
What is the relationship between LUPs and affordability?
   A bath Tub curve
What would the revenue from an empty homes tax be in the current situation?
  A lot

@@

setwd(file.path(RegionsComp, "Region Wales"))
list.files()

#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.

CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))

#includes the zero class which is descibeed as
#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
    StructureData()

#Strangely low numbers checking
# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(3,5:6))

#It seems Conwy really is this short on the discounts
ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
  rename(Postcode = geo_postcode) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2,4))

DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(c(8:9,11,13))

WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
    StructureData(2:5)

#Pembrokeshire didn't send all the data
PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData(3)

FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData()

@@

#Scrub the names

Remove LSOA that belong to another LAD

for(i in ls(pattern = "DATA")){

  Temp <-get(i) %>% 
    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
    summarise_all(funs(first)) %>% 
    group_by(LAD11CD) %>% #Remove LAD data that is not from this lad. Occaisonly a few lsoa from other LADs get in and cause problems
    mutate(LADCount = n()) %>% ungroup %>%
    filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
    select(-LADCount)

  assign(i, Temp)

@@

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:MSOALowuseClass)) %>%
  group_by(MSOA11CD) %>% # ward code is used for consistency
  summarise(
    #MSOA11CD = first(MSOA11CD), #MSOA is kept to allow joining of income
    LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 50))

@@

#Is n
unaffordLAD <- unafford %>%
  rename(LAD11CD = Local.authority.code) %>%
  group_by(LAD11CD) %>%
  mutate(TotInc = Yearly.income*Homes) %>%
  summarise(TotInc = sum(TotInc),
            Homes = sum(Homes)) %>%
  mutate(meanInc = TotInc/Homes)

@@

CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA11CD) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

@@

MakeLeaflet(WestminsterLONDATA)

#MSOA version

NorthDevonDATA %>%
 # left_join(select(BootDeetsMean, MSOA11CD, AffordRatio)) %>%
 # mutate(LowUsePerc = AffordRatio/mean(AffordRatio)) %>% 
  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
  filter(LAD11NM =="Kensington and Chelsea") %>% 
  MakeLeaflet()

  MakeLeaflet(NorthDevonDATA)
